Detection of an Intrinsic Color Parameter within the Type~Ia Supernovae of the Nearby Supernova Factory

### 2016-10-03 forgerard.tex
Moving on...

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{0.0009}_{-0.0009}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0015^{0.0006}_{-0.0006}$
&
$0.0015^{0.0005}_{-0.0005}$
&
$0.0026^{0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{   1.0}_{  -0.5}$
&
$   0.1^{   0.1}_{  -0.2}$
&
$   0$
&
$  -0.0^{   0.1}_{  -0.1}$
&
$   0.7^{   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{ 0.003}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
&
$ 0.019^{ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{  0.05}_{ -0.05}$
&
$ -0.01^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.24^{  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{0.0012}_{-0.0011}$
&
$-0.0000^{0.0010}_{-0.0009}$
&
$0.0005^{0.0008}_{-0.0008}$
&
$0.0005^{0.0007}_{-0.0007}$
&
$-0.0003^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{  2.33}_{ -1.90}$
&
$ -0.34^{  1.60}_{ -1.20}$
&
$  0$
&
$ -0.11^{  0.29}_{ -0.27}$
&
$ -0.84^{  1.66}_{ -1.27}$
\\
$\gamma^0_X$
&
$ 62.16^{  3.68}_{ -3.52}$
&
$ 50.39^{  3.05}_{ -2.96}$
&
$ 37.38^{  2.58}_{ -2.52}$
&
$ 28.71^{  2.31}_{ -2.25}$
&
$ 20.61^{  2.15}_{ -2.11}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{  0.06}_{ -0.05}$
&
$  0.35^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.75^{  3.39}_{ -4.14}$
&
$-11.82^{  2.78}_{ -3.35}$
&
$-14.26^{  2.38}_{ -2.73}$
&
$-13.35^{  2.09}_{ -2.30}$
&
$-11.91^{  2.01}_{ -2.15}$
\\
${\gamma^1_X/\gamma^1_2-1}$
&
$ -0.31^{  0.17}_{ -0.18}$
&
$ -0.17^{  0.09}_{ -0.10}$
&
$  0$
&
$ -0.07^{  0.05}_{ -0.04}$
&
$ -0.17^{  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{ 0.012}_{-0.012}$
&
$ 0.033^{ 0.007}_{-0.007}$
&
$ 0.021^{ 0.004}_{-0.006}$
&
$ 0.012^{ 0.007}_{-0.008}$
&
$ 0.044^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters \label{global:tab}}
\end{table}

@@

\section{Intrinsic Color}
\label{model2:sec}
Analysis of the data using the model presented in \S\ref{model:sec} drew out parameter values consistent
with two-parameter dust models.  We now consider an extension to the model that accommodate an additional
color parameter.
The new model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$ to the absolute magnitudes.
Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes through $\delta$. 
Although
this term is introduced through the absolute rather than observed magnitude,
practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
degeneracy, for convenience we refer to this term as ``intrinsic''.

To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
\end{equation}
The first specifies the definition of zero color.   The latter two confine possible magnitude
variations to those unattributablabe to 
the $\gamma k$ terms (i.e.\ dust); without this pragmatic condition $\delta D$  
was degenerate and tended toward $\gamma k$ in the fit.  The initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.

The resulting posteriors of our parameters are given in Table~\ref{}
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters \label{global2:tab}}
\end{table}

For dust and our model, possible magnitudes are confined to a plane on the 5-dimensional magnitude space.
It turns out that the planes for both models are nearly parallel, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.16 & 2.82 \\
0.74 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The distribution of both sources of color excess $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
 $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
Recall that our boundary conditions set the means of both distributions to zero. 
The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
%-----
0.079
and 0.015
%-----
mag respectively.
The range of $B-V$ colors is $\sim 5$ times larger for the external contribution. 
Both distributions are non-Gaussian with sharp rises in the blue and extended tails in the red, consistent
with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=3.2in]{output11/ebv.pdf}
   \caption{Ideograms of the external $E_\gamma(B-V) =(\gamma_B-\gamma_V)k$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
   \label{ebv:fig}}
\end{figure}

\section{Discussion}
\label{discussion:sec}
We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and distinct intrinsic and
extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
affect supernova magnitudes and colors.  The external color parameter has behavior consistent with  $R^F_V=2.97$ \citet{1999PASP..111...63F} dust,
whereas the internal color parameter is inconsistent with dust or a blackbody.  This model  does an excellent job in
describing SN~2014J, a supernova not used in the training that has atypical colors.

\color{red}
Our model does not explicitly include light-curve shape, which is known to track SN~Ia diversity.
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss from the neglect of $X_1$.
We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: the values
for
$\zeta$ are consistent with zero to $2\sigma$, while the $\alpha$'s and $\beta$'s remain significantly
non-zero.  
Nevertheless, there 
appear to be non-linear correlations 
between $X_1$ and the residuals between observed and model-predicted colors, as seen in
Figure~\ref{x1res:fig}.
Extending our model to include non-linear terms is a direction for future work.
\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output11/x1si.pdf}
   \includegraphics[width=2.8in]{output11/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output11/residualx1.pdf}
    \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
            of the SALT2 light-curve shape parameter $X_1$.  For reference a dotted line is plotted at zero difference.}
   \label{x1res:fig}}
\end{figure}

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0041^{0.0010}_{-0.0010}$
&
$0.0015^{0.0008}_{-0.0008}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0015^{0.0006}_{-0.0006}$
&
$0.0027^{0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.6^{   0.9}_{  -0.4}$
&
$  -0.1^{   0.1}_{  -0.2}$
&
$   0.0^{   0.0}_{   0.0}$
&
$  -0.1^{   0.1}_{  -0.1}$
&
$   0.7^{   0.8}_{  -0.3}$
\\
$\beta_X$
&
$ 0.033^{ 0.006}_{-0.006}$
&
$ 0.025^{ 0.005}_{-0.005}$
&
$ 0.022^{ 0.004}_{-0.004}$
&
$ 0.019^{ 0.003}_{-0.003}$
&
$ 0.016^{ 0.003}_{-0.003}$
\\
${\beta_X/\beta_V-1}$
&
$  0.50^{  0.13}_{ -0.12}$
&
$  0.14^{  0.07}_{ -0.07}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.14^{  0.03}_{ -0.03}$
&
$ -0.28^{  0.06}_{ -0.06}$
\\
$\eta_X$
&
$0.0001^{0.0011}_{-0.0011}$
&
$0.0003^{0.0009}_{-0.0009}$
&
$0.0008^{0.0008}_{-0.0008}$
&
$0.0007^{0.0007}_{-0.0007}$
&
$-0.0001^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.49^{  1.15}_{ -1.55}$
&
$ -0.39^{  0.84}_{ -0.99}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.14^{  0.19}_{ -0.18}$
&
$ -0.83^{  0.78}_{ -0.96}$
\\
$\zeta_X$
&
$ 0.004^{ 0.039}_{-0.040}$
&
$-0.005^{ 0.033}_{-0.033}$
&
$-0.028^{ 0.028}_{-0.028}$
&
$-0.013^{ 0.024}_{-0.024}$
&
$-0.029^{ 0.021}_{-0.021}$
\\
${\zeta_X/\zeta_V-1}$
&
$  -0.7^{   1.1}_{  -1.7}$
&
$  -0.5^{   0.6}_{  -1.2}$
&
$   0.0^{   0.0}_{   0.0}$
&
$  -0.4^{   0.3}_{  -0.5}$
&
$  -0.1^{   0.6}_{  -0.4}$
\\
${\gamma_X/\gamma_V-1}$
&
$  0.64^{  0.06}_{ -0.05}$
&
$  0.34^{  0.03}_{ -0.03}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$R_X$
&
$  4.78^{  0.52}_{ -0.45}$
&
$  3.91^{  0.42}_{ -0.37}$
&
$  2.91^{  0.33}_{ -0.29}$
&
$  2.23^{  0.27}_{ -0.24}$
&
$  1.60^{  0.22}_{ -0.20}$
\\
${\delta_X/\delta_V-1}$
&
$ -0.38^{  0.17}_{ -0.19}$
&
$ -0.23^{  0.10}_{ -0.10}$
&
$  0.00^{  0.00}_{  0.00}$
&
$ -0.07^{  0.04}_{ -0.04}$
&
$ -0.17^{  0.09}_{ -0.09}$
\\
$R_{\delta X}$
&
$ -2.78^{  1.23}_{ -2.20}$
&
$ -3.49^{  1.22}_{ -2.38}$
&
$ -4.49^{  1.35}_{ -2.78}$
&
$ -4.17^{  1.23}_{ -2.55}$
&
$ -3.72^{  1.12}_{ -2.28}$
\\
$\sigma_X$
&
$ 0.060^{ 0.013}_{-0.012}$
&
$ 0.033^{ 0.007}_{-0.007}$
&
$ 0.018^{ 0.005}_{-0.008}$
&
$ 0.014^{ 0.006}_{-0.008}$
&
$ 0.044^{ 0.006}_{-0.005}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters including $X_1$ \label{globalx1:tab}}
\end{table}

\citet{2014ApJ...789...32B, 2015MNRAS.453.3300A} deduce a wide range of dust behavior $1.5<R^F_V<3$ encountered by the SN~Ia population.
\citet{2011ApJ...731..120M, 2011ApJ...729...55F} and the above authors
find that supernovae with large $E_o(B-V)$ 
preferentially exhibit low $R^F_V$. 
\color{red}
\citet{2016arXiv160904470M} demonstrate how biased $R_V$ determinations can arise from unaccounted intrinsic color dispersion.
In our model internal and external effects for each supernova  conflate into an effective color excess
$E_{eff}(X-V) = E_\gamma(X-V) + E_\delta(X-V)$ and effective $V$ extinction $A_{eff,V} = \gamma_V k  + \delta_V D$.
Recall that the colors where $E_\gamma(B-V)=0$,  $E_\delta(B-V)=0$ are free and arbitrarily
fixed using the  boundary conditions $\langle \Delta \rangle = 0$, $\langle k \rangle = 0$:
there is no unique value for the statistic $R_{eff,V} = A_{eff,V} /E_{eff}(B-V)$, as it depends on the choice of  boundary condition.

>>>>

\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0043^{0.0009}_{-0.0009}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0015^{0.0006}_{-0.0006}$
&
$0.0015^{0.0005}_{-0.0005}$
&
$0.0026^{0.0005}_{-0.0004}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.9^{   1.0}_{  -0.5}$
&
$   0.1^{   0.1}_{  -0.2}$
&
$   0$
&
$  -0.0^{   0.1}_{  -0.1}$
&
$   0.7^{   0.7}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{ 0.003}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
&
$ 0.019^{ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{  0.05}_{ -0.05}$
&
$ -0.01^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.19^{  0.01}_{ -0.01}$
&
$ -0.24^{  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{0.0012}_{-0.0011}$
&
$-0.0000^{0.0010}_{-0.0009}$
&
$0.0005^{0.0008}_{-0.0008}$
&
$0.0005^{0.0007}_{-0.0007}$
&
$-0.0003^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{  2.33}_{ -1.90}$
&
$ -0.34^{  1.60}_{ -1.20}$
&
$  0$
&
$ -0.11^{  0.29}_{ -0.27}$
&
$ -0.84^{  1.66}_{ -1.27}$
\\
$\gamma^0_X$
&
$ 62.16^{  3.68}_{ -3.52}$
&
$ 50.39^{  3.05}_{ -2.96}$
&
$ 37.38^{  2.58}_{ -2.52}$
&
$ 28.71^{  2.31}_{ -2.25}$
&
$ 20.61^{  2.15}_{ -2.11}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{  0.06}_{ -0.05}$
&
$  0.35^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.75^{  3.39}_{ -4.14}$
&
$-11.82^{  2.78}_{ -3.35}$
&
$-14.26^{  2.38}_{ -2.73}$
&
$-13.35^{  2.09}_{ -2.30}$
&
$-11.91^{  2.01}_{ -2.15}$
\\
${\gamma^1_X/\gamma^1_2-1}$
&
$ -0.31^{  0.17}_{ -0.18}$
&
$ -0.17^{  0.09}_{ -0.10}$
&
$  0$
&
$ -0.07^{  0.05}_{ -0.04}$
&
$ -0.17^{  0.10}_{ -0.09}$
\\
$\sigma_X$
&
$ 0.060^{ 0.012}_{-0.012}$
&
$ 0.033^{ 0.007}_{-0.007}$
&
$ 0.021^{ 0.004}_{-0.006}$
&
$ 0.012^{ 0.007}_{-0.008}$
&
$ 0.044^{ 0.005}_{-0.004}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters of the 2-Parameter Extrinsic Model \label{global:tab}}
\end{table}

@@

\section{Intrinsic Color}
\label{model2:sec}
Analysis of the data using the model presented in \S\ref{model:sec} draws out parameter values consistent
with two-parameter dust models.  We now consider an extension to our model that accommodates an additional
color parameter.
The new model is written as
\begin{equation}
\begin{pmatrix}
U\\B\\V\\R\\I
\end{pmatrix}
\sim \mathcal{N}
\left(
\Delta +
\begin{pmatrix}
c_0+\alpha_0 EW_{Ca} + \beta_0 EW_{Si} + \eta_0 \lambda_{Si} + \delta_0 D\\
c_1+\alpha_1 EW_{Ca} + \beta_1 EW_{Si} + \eta_1 \lambda_{Si} + \delta_1 D \\
c_2+\alpha_2 EW_{Ca} + \beta_2 EW_{Si} + \eta_2 \lambda_{Si} + \delta_2 D\\
c_3+\alpha_3 EW_{Ca} + \beta_3 EW_{Si} + \eta_3 \lambda_{Si} + \delta_3 D\\
c_4+\alpha_4 EW_{Ca} + \beta_4 EW_{Si}+ \eta_4 \lambda_{Si} + \delta_4 D
\end{pmatrix}
,C_{c}
\right)
\label{ewsiv:eqn}
\end{equation}
\begin{equation}
\begin{pmatrix}
U_o\\B_o\\ V_o\\R_o\\I_o\\EW_{Si, o}\\ EW_{Ca, o} \\ \lambda_{Si, o}
\end{pmatrix}
\sim \mathcal{N}
\left(
\begin{pmatrix}
U +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\B +\gamma^0_{1} k_0 +\gamma^1_{1} k_1 \\
V+\gamma^0_{2} k_0+\gamma^1_{2} k_1\\R+\gamma^0_{3} k_0 + \gamma^1_{3} k_1\\I+\gamma^0_{4} k_0+\gamma^1_{4} k_1\\
EW_{Si}\\ EW_{Ca} \\ \lambda_{Si}
\end{pmatrix}
,C
\right).
\label{dust:eqn}
\end{equation}
In all aspects it is identical to the previous model except for the addition of the term $\delta D$ toward the mean
absolute magnitudes.
Each supernova has an intrinsic $D$ parameter that influences absolute magnitudes with strength $\delta$. 
Although
this term is introduced through the absolute rather than observed magnitudes,
practically identical results are obtained when it is placed alongside the extrinsic $\gamma k$ terms.  Despite this
degeneracy, this term is referred to as ``intrinsic''.

To constrain the new degrees of freedom and degeneracies inherent in the model we impose that
$D+1/N$ be a simplex to break the 
degeneracy  $\delta \rightarrow a\delta$, $D \rightarrow a^{-1}D$.
Furthermore we impose
\begin{equation}
\langle D\rangle=0,  \delta \cdot \gamma^0=0, \delta \cdot \gamma^1=0.
\end{equation}
The first specifies the definition of zero color.   The latter two confine possible magnitude
variations to those that cannot be attributed to 
the $\gamma k$ terms (i.e.\ dust); practically it is difficult to break the degeneracies between $\delta D$  
and $\gamma k$ in the fit. 
Unlike for the $\gamma$'s, there is no condition on the sign of $\delta_0$,
so that the posterior has degenerate solutions with sign flips of $\delta$ and $D$.
In the running of the Monte Carlo, the initial conditions for
$\gamma^0$ and $\gamma^1$ were set to be in the neighborhood of the best fit of \S\ref{model:sec}.

The resulting credible intervals of our parameters are given in Table~\ref{global2:tab}.  Comparison with the
results of the 2-parameter extrinsic model given in Table~\ref{global:tab} shows that common parameters
are consistent well within 1$\sigma$ uncertainties.  The most significant changes of note are in the standard
deviations of the residuals in the $V$ and $I$ bands.
\begin{table}
\centering
\begin{tabular}{|c|c|c|c|c|c|}
\hline
& $X=U$ &$B$&$V$&$R$&$I$\\ \hline
$\alpha_X$
&
$0.0044^{0.0009}_{-0.0009}$
&
$0.0016^{0.0007}_{-0.0007}$
&
$0.0016^{0.0006}_{-0.0006}$
&
$0.0015^{0.0005}_{-0.0005}$
&
$0.0026^{0.0005}_{-0.0005}$
\\
${\alpha_X/\alpha_V-1}$
&
$   1.8^{   0.9}_{  -0.4}$
&
$   0.0^{   0.1}_{  -0.2}$
&
$   0$
&
$  -0.0^{   0.1}_{  -0.1}$
&
$   0.6^{   0.6}_{  -0.3}$
\\
$\beta_X$
&
$ 0.032^{ 0.003}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.003}$
&
$ 0.025^{ 0.002}_{-0.002}$
&
$ 0.020^{ 0.002}_{-0.002}$
&
$ 0.019^{ 0.002}_{-0.002}$
\\
${\beta_X/\beta_V-1}$
&
$  0.26^{  0.05}_{ -0.05}$
&
$ -0.01^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.19^{  0.01}_{ -0.02}$
&
$ -0.24^{  0.03}_{ -0.03}$
\\
$\eta_X$
&
$-0.0002^{0.0012}_{-0.0011}$
&
$0.0000^{0.0010}_{-0.0009}$
&
$0.0005^{0.0008}_{-0.0008}$
&
$0.0005^{0.0007}_{-0.0007}$
&
$-0.0003^{0.0006}_{-0.0006}$
\\
${\eta_X/\eta_V-1}$
&
$ -0.40^{  2.19}_{ -1.84}$
&
$ -0.36^{  1.57}_{ -1.19}$
&
$  0$
&
$ -0.12^{  0.27}_{ -0.25}$
&
$ -0.89^{  1.72}_{ -1.35}$
\\
$\gamma^0_X$
&
$ 62.53^{  3.64}_{ -3.63}$
&
$ 50.74^{  3.08}_{ -3.03}$
&
$ 37.67^{  2.62}_{ -2.60}$
&
$ 28.89^{  2.32}_{ -2.33}$
&
$ 20.62^{  2.15}_{ -2.16}$
\\
${\gamma^0_X/\gamma^0_V-1}$
&
$  0.66^{  0.06}_{ -0.05}$
&
$  0.35^{  0.03}_{ -0.03}$
&
$  0$
&
$ -0.23^{  0.01}_{ -0.01}$
&
$ -0.45^{  0.03}_{ -0.03}$
\\
$\gamma^1_X$
&
$ -9.93^{  3.53}_{ -4.16}$
&
$-11.80^{  2.91}_{ -3.44}$
&
$-14.25^{  2.45}_{ -2.72}$
&
$-13.39^{  2.15}_{ -2.29}$
&
$-12.05^{  1.97}_{ -2.14}$
\\
${\gamma^1_X/\gamma^1_2-1}$
&
$ -0.30^{  0.18}_{ -0.19}$
&
$ -0.17^{  0.09}_{ -0.10}$
&
$  0$
&
$ -0.06^{  0.05}_{ -0.04}$
&
$ -0.16^{  0.10}_{ -0.08}$
\\
${{\delta_X/\delta_I-1}}$
&
$ -0.61^{  0.47}_{ -0.18}$
&
$ -1.21^{  0.25}_{ -0.77}$
&
$ -1.76^{  0.16}_{ -0.20}$
&
$ -1.17^{  0.29}_{ -0.20}$
&
$  0$
\\
$\sigma_X$
&
$ 0.059^{ 0.013}_{-0.013}$
&
$ 0.031^{ 0.007}_{-0.008}$
&
$ 0.017^{ 0.005}_{-0.007}$
&
$ 0.012^{ 0.006}_{-0.007}$
&
$ 0.039^{ 0.005}_{-0.005}$
\\
\hline
\end{tabular}
\caption{68\% credible Intervals for the Global Fit Parameters of the Intrinsic-Extrinsic Model\label{global2:tab}}
\end{table}

We find that the newly fitted $\delta$ parameters have almost identical association with the Fitzpatrick dust law, in that
\begin{equation}
\begin{pmatrix}
 \frac{\gamma^0_X}{\gamma^0_1-\gamma^0_2} \\
\frac{\gamma^1_X}{\gamma^1_1-\gamma^1_2} 
\end{pmatrix}=
\begin{pmatrix}
1.16 & 2.82 \\
0.74 & -5.43
\end{pmatrix} 
\begin{pmatrix}
a(X) \\
b(X)
\end{pmatrix}+
\vec{\epsilon},
\end{equation}
where the residual $\vec{\epsilon}$''s perpendicular to the Fitzpatrick plane
contribute  2\% and 5\% to the total  length of the vector.

The distribution of both sources of color excess $E(B-V)$ and
 $E_\delta(B-V) = (\delta_B-\delta_V)D$ are shown as the ideograms in Figure~\ref{ebv:fig}.
Recall that our boundary conditions set the means of both distributions to zero. 
The standard deviations of $E_\gamma(B-V)$ and $E_\delta(B-V)$ are
%-----
0.081
and 0.010
%-----
mag respectively.
The range of $B-V$ colors is $\sim 8$ times larger for the external contribution. 
Both distributions are non-Gaussian, that of $E(B-V)$ has a sharp rise in the blue and an extended tail in the red, consistent
with the expectation for extinction due to host-galaxy dust \citep{1998ApJ...502..177H}.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output15/ebv.pdf}
   \includegraphics[width=2.8in]{output15/ebv_delta.pdf}
      \caption{Left: Ideograms of the external $E(B-V)$ and
   internal $E_\delta(B-V) = (\delta_B-\delta_V)D$  contributions to color excess  for the supernovae in our sample.
   Right: Ideogram of $E_\delta(B-V)$ on an enlarged scale.
   \label{ebv:fig}}
\end{figure}
The significance of the $\delta$ parameters is shown pictorially
in Figure~\ref{deltacorner:fig}. The left plot shows the $\delta$ posteriors, which is bimodal due to the parity symmetry.  The probability
of the null result $\delta_X=0$ for all $X$, lies on a
$>98\%$-contour.  The right plot shows values of $\delta_X/\delta_I-1$, which nulls out the parity symmetry and has significant non-zero values.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output15/delta_corner.pdf}
      \includegraphics[width=2.8in]{output15/deltaratio.pdf}
   \caption{Significance of the non-zero values of $\delta$.  Left: Posterior contours for $\delta$.  The bimodality is due to the degenerate solution due to sign change.
   Right: $\delta_X/\delta_I-1$, which as a ratio is insensitive to the degeneracy.
   \label{deltacorner:fig}}
\end{figure}

\section{Discussion}
\label{discussion:sec}
We model SNe~Ia broadband optical peak magnitudes allowing for correlations with spectral features at peak and
extrinsic color parameters.  Analyzing SNfactory data with the model, we find significant evidence that the above parameters do
affect supernova magnitudes and colors.  The external color parameters are consistent with \citet{1999PASP..111...63F} dust
with $R^F_V=2.43$.  This model  does an excellent job in
describing SN~2014J, a supernova not used in the training that has atypical colors.  An extended version
of the model retains the features of the first model, but now with strong evidence for a new parameter related to supernova
colors.

\color{red}
Our models do not explicitly include light-curve shape, which is known to track SN~Ia diversity.
We now examine this in more depth using the intrinsic--extrinsic model of \S\ref{model2:sec}.
The correlation between $EW_{Si}$ and the SALT2 $X_1$ light-curve shape parameter is verified
for our sample, as shown in Figure~\ref{x1:fig}.
On the other hand, there is no such correlation seen between $E_\delta(B-V)$ and $X_1$. 
Our magnitude residuals $\sigma_X$ are comparable to those of SALT2
\citep{2010A&A...523A...7G}, showing that our model exhibits no clear loss from the neglect of $X_1$.
We  run an extension of our model to include light-curve shape by adding a new linear term $\zeta X_1$; the credible intervals
from this analysis are given in Table~\ref{globalx1:tab}; no significant changes are seen. 
In fact, light-curve shape is not a strong predictor of supernova magnitude relative to the spectral features: only $\zeta_R/\zeta_V$
has a non-zero value at $>2\sigma$.
The parameters that describe intrinsic color $\delta$ remain significantly non-zero.

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=2.8in]{output15/x1si.pdf}
   \includegraphics[width=2.8in]{output15/x1D.pdf}
    \caption{\textcolor{red}{Left: SALT2 $X_1$ versus $EW_{Si}$.  Right: $X_1$ versus $E_\delta(B-V)$.}
   \label{x1:fig}}
\end{figure}

\begin{figure}[htbp] %  figure placement: here, top, bottom, or page
   \centering
   \includegraphics[width=5in]{output15/residualx1.pdf}
    \caption{\textcolor{red}{Differences between observed colors and the colors predicted from the analysis, as a function
            of the SALT2 light-curve shape parameter $X_1$.  For reference a dotted line is plotted at zero difference.}
   \label{x1res:fig}}
\end{figure}
